The Country-level Impact of Educational Features on the Rate of Entrepreneurship - Data Gathering and Analysis

### 2014-11-13 GEMDataSource.Rmd
Update GEMDataSource.Rmd

In order to scrape our data, we used repmis, tidyr, reshape2, plyr, WDI, stargazer and Zelig packages. We then imported one dataset per variable mentioned above:
GEM Established Entrepreneurship Rate
GEM Nascent Entrepreneurship Rate
GEM Entrepreneurial Intention
GEM Perceived Capabilities
GEM Fear of Failure
GEM Perceived Opportunities
GDP Annual Growth Rate

>>>>

In order to scrape our data, we used repmis, tidyr, reshape2, plyr, WDI, stargazer and Zelig packages. We then imported one dataset per variable mentioned above:

GEM Established Entrepreneurship Rate

GEM Nascent Entrepreneurship Rate

GEM Entrepreneurial Intention

GEM Perceived Capabilities

GEM Fear of Failure

GEM Perceived Opportunities

GDP Annual Growth Rate
